Carbonate chemistry at Ny-Ålesund

### 2022-08-11 awipev-CO2.Rmd
figure finalized

# for paper
at_s <- d_all_at_discrete %>% 
  dplyr::select(sal_fb_mix, at) %>% 
  drop_na() %>% 
  ggplot(aes(x = sal_fb_mix, y = at)) +
  geom_point(col="blue", size = 0.5) +
  labs(x= latex2exp::TeX("Salinity"),
       y= latex2exp::TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"))  +
  ggpmisc::stat_ma_line(method = "lmodel2:OLS", se = FALSE, size = 1) +
  #ggpmisc::stat_ma_eq(method = "lmodel2:OLS", aes(label = after_stat(eq.label))) +
  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio=1) + 
  coord_fixed()
at_s
ggsave(filename = "figures/figures/at_s.png", plot = at_s, width = 25, height = 25, units = "cm")

@@

The relationship between titrated total alkalinity (references) and
salinity is very good with an r2 of
`r round(reg$fit$rsquare, digits = 2)`. Need to compare with other relationships from the literature.

@@

The relationship between the measured (Contros) and calculated pCO2
(blue line) is relatively poor. It is far from the 1:1 relationship
(black dashed line). The slope is
`r signif(reg$fit$regression.results[2,3], 3)`) and its 95% confidence
interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)`.

@@

pHspec_pHcalc <- d_all %>% 
  dplyr::select(ph_s_sf_temp_insi, pHint_tot_sf) %>% 
  drop_na() %>% 
  ggplot(aes(x = ph_s_sf_temp_insi, y = pHint_tot_sf)) +
  geom_point(col="blue", size = 0.5) +
  xlim(8.05, 8.18) + ylim(8.05, 8.18) +
  labs(x="Spectrophotometric pH",
       y= "SeaFET pH")  +
  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
  #ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label), digits = 4)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
ggsave(filename = "figures/pHspec_pHcalc.png", plot = pHspec_pHcalc, width = 25, height = 25, units = "cm")
```

>>>>

# for paper
at_s <- d_all_at_discrete %>% 
  dplyr::select(sal_fb_mix, at) %>% 
  drop_na() %>% 
  ggplot(aes(x = sal_fb_mix, y = at)) +
  geom_point(col="blue", size = 0.5) +
  labs(x= latex2exp::TeX("Salinity"),
       y= latex2exp::TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"))  +
  ggpmisc::stat_ma_line(method = "lmodel2:OLS", se = FALSE, size = 1) +
  #ggpmisc::stat_ma_eq(method = "lmodel2:OLS", aes(label = after_stat(eq.label))) +
  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio=1) + 
  coord_fixed()
ggsave(filename = "figures/figures/at_s.png", plot = at_s, width = 25, height = 25, units = "cm")

@@

The relationship between titrated total alkalinity (references) and
salinity is very good with an r2 of
`r round(reg$fit$rsquare, digits = 2)` (`r N = reg$fit$n`). Need to compare with other relationships from the literature.

@@

The relationship between the measured (Contros) and calculated pCO2
(blue line) is relatively poor. It is far from the 1:1 relationship
(black dashed line). The slope is
`r signif(reg$fit$regression.results[2,3], 3)`) and its 95% confidence
interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)  (`r N = reg$fit$n`)`.

@@

pHspec_pHcalc <- d_all %>% 
  dplyr::select(ph_s_sf_temp_insi, pHint_tot_sf) %>% 
  drop_na() %>% 
  ggplot(aes(x = ph_s_sf_temp_insi, y = pHint_tot_sf)) +
  geom_point(col="blue", size = 0.5) +
  xlim(8.05, 8.18) + ylim(8.05, 8.18) +
  labs(x="Spectrophotometric pH",
       y= "SeaFET pH")  +
  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
  #ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label), digits = 4)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
ggsave(filename = "figures/pHspec_pHcalc.png", plot = pHspec_pHcalc, width = 25, height = 25, units = "cm")
```
The relationship between spectrophotometric pH and SeaFET pH) and 
(blue line) is relatively good The slope is
`r signif(reg$fit$regression.results[2,3], 3)`) and its 95% confidence
interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)  (`r N = reg$fit$n`)`.
